---
title: "Draft R Markdown document"
author: "Your Name"
format: html
editor:
    markdown:
        wrap: 72
        canonical: true
---

```{r setup}
targets::tar_config_set(store = here::here("_targets"))
library(tidyverse)
library(targets)
library(tidymodels)
source(here::here("R/functions.R"))
lipidomics <- targets::tar_read(lipidomics)
```

## Results

```{r}
targets::tar_read(df_stats_by_metabolite) %>%
  mutate(MeanSD = glue::glue("{value_mean} ({value_sd})")) %>%
  select(Metabolite = metabolite, `Mean SD` = MeanSD) %>%
  knitr::kable(caption = "Descriptive Statistics of the metabolites")
```

```{r}
targets::tar_read(fig_metabolite_distribution)
```

# Building the model

```{r}
log_reg_specs <- logistic_reg() %>%
  set_engine("glm")
log_reg_specs

lipidomics %>%
  column_values_to_snake_case(., metabolite) %>%
  metabolites_to_wider()
```

```{r}
recipe(class ~ metabolite_lipid_ch_3_1 + age + gender, data = lipidomics_wide)
```

```{r}
recipe(lipidomics_wide) %>%
  update_role(metabolite_lipid_ch_3_1, age, gender, new_role = "predictor") %>%
  update_role(class, new_role = "outcome") %>%
  step_normalize(starts_with("metabolite_"))
```

```{r}
recipe_specs <- lipidomics_wide %>%
  create_recipe_spec(metabolite_lipid_ch_3_1)
recipe_specs
```

```{r}
workflow() %>% 
    add_model(log_reg_specs) %>% 
    add_recipe(recipe_specs)

model_workflow <- create_model_workflow(log_reg_specs, recipe_specs)
model_workflow
```

#---------------------------

# Mal Own notes

-   recipes is transformations
-   engine is model

## This is poorly formatted

-   This is item 1
-   This is item 2

# List of notes

-   Her vil R selv formattere, så hvis der ikke er mellemrum nok vil R
    selv indføre det pga ting vi indsatte i headeren (canonical: true)
-   Generelt vil R med dette canocicla sørge for det er mellemrum mellem
    tingene
-   Wrap 72 is visual mode

If it is a part of the build, it will be joined as a package. A part of
the workflow will be joined as a Suggestion.

If things does not work, try renv::install()

.libPaths() = tjek om du er i dit projekt, vi vil gerne være i renv

# Comands for targets

-   targets::tar_make() \<- incorporating into pipeline
-   targets::tar_visnetwork()
-   targets::tar_outdated()
-   targets::tar_read()
-   styler:::style_active_file()
